Web Service Wrapping, Discovery and Consumption --- More Power to the End-User

### 2010-06-15 trunk/papers/icsoc2010/paper_sec_catalogue.tex
updating catalogue section
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@887 d8b0c59b-6544-0410-94d9-83a5658a058e

The architecture comprises a RDF store used for persistence, a business layer dealing with the model and reasoning, and public facade providing the core functionality as a RESTful API, and a SPARQL endpoint accessing directly the RDF store. This presentation layer is aimed to interact with the FAST Gadget Visual Storyboard, or any other third-party application.

The RESTful API and the SPARQL endpoint are part of the presentation layer. The SPARQL endpoint is offered using the SPARQL protocol service as defined in the SPROT specification \cite{sprot} and is aimed to enable third-party developers to query directly the knowledge base using SPARQL queries. This feature is supported by the Sesame RESTful HTTP interface for SPARQL Protocol for RDF.

@@

The persistence layer provides an API allowing to work with a standard set of objects representing the model. The interaction with the underlying RDF store is made via RDF2Go, an abstraction over triple (and quad) stores, which allows to program against rdf2go interfaces and choose any RDF store implementation. This allows having a completely extensible and configurable framework for storage mechanisms, inferencers, RDF file formats, query result formats and query languages.

>>>>

The architecture comprises an RDF store used for persistence, a business layer dealing with the model and reasoning, and a public facade providing the core functionality as a RESTful API, as well as a SPARQL endpoint accessing the RDF store directly. This presentation layer is aimed to interact with the FAST Gadget Visual Storyboard (see Sect.~\ref{sec:use_case}), or any other third-party application.

The RESTful API and the SPARQL endpoint are part of the presentation layer. The SPARQL endpoint is offered using the SPARQL protocol service as defined in the SPROT specification~\cite{sprot} and is aimed to enable third-party developers to directly query the knowledge base using SPARQL queries. This feature is supported by the Sesame RESTful HTTP interface for SPARQL Protocol for RDF.

@@

The persistence layer provides an API allowing to work with a standard set of objects representing the model. The interaction with the underlying RDF store is made via RDF2Go, an abstraction over triple (and quad) stores, which allows to program against RDF2Go interfaces and choose any RDF store implementation. This allows having a completely extensible and configurable framework for storage mechanisms, inferencers, RDF file formats, query result formats and query languages.

### 2010-06-15 trunk/papers/icsoc2010/paper_ssec_linked_data.tex
updating catalogue section
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@887 d8b0c59b-6544-0410-94d9-83a5658a058e

The recently success of the Web of Data has influenced the way information is now published on the web, and has been widely adopted by the academic community, large companies such as The New York Times and BBC, and national governments such as US and UK made public commitments toward open data. The main aim of the linking data is to find other related data based upon previously known data, in terms of the connections or links between them. We apply this concept in order to provide metadata about the web services as linked data, following the principles as originally defined in \cite{bizer_ijswis2009}, in order to make them available to arbitrary third-party applications. Each web service is identified by an HTTP URI and hosted in the publishing platform so that it can be dereferenced through the same URI. For each building block, data is available in representations in different standard formats such as JSON (for communication with the GVS), RDF/XML, Turtle, or even HTML+RDFa as a human-readable version. The principles and best practices proposed in \cite{berrueta2008} and \cite{sauermann2008cool_uris} are also taken into account, these representations are served based on the request issued by the requesting agent, using a technique called \emph{content negotiation}. As required by the forth rule of linked data, individual building blocks link to other data on the web, thereby preventing so-called isolated ``data islands''.

>>>>

The recently success of the Web of Data has influenced the way information is now published on the web, and has been widely adopted by the academic community. Also large companies such as The New York Times and BBC, and national governments such as US and UK made public commitments toward open data. The main aim of the linking data is to find other related data based upon previously known data, in terms of the connections or links between them. We apply this concept in order to provide metadata about the web services as linked data, following the principles as defined in~\cite{bizer_ijswis2009}, in order to make them available to arbitrary third-party applications. Each web service is identified by an HTTP URI and hosted in the publishing platform so that it can be dereferenced through the same URI. For each building block, data is available in representations in different standard formats such as JSON (for communication with the applications such as the widget designer shown in Fig.~\ref{fig:fast_architecture}), RDF/XML, Turtle, or even HTML+RDFa as a human-readable version. The principles and best practices proposed in \cite{berrueta2008} and \cite{sauermann2008cool_uris} are also taken into account, so that these representations are served based on the request issued by the requesting agent, using a technique called \emph{content negotiation}. As suggested by linked data principles, individual building blocks link to other data on the web, thereby preventing so-called isolated ``data islands''.
